%-------------------------
% Resume in Latex
% Author : Shaoqing Yu (Shawn)
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex,ocgcolorlinks]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{3pt}
    \textit{\small#3}   
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://www.linkedin.com/in/yushaoqing}{\Large Shaoqing Yu (Shawn)}} & Email : \href{mailto:syu702@aucklanduni.ac.nz}{syu702@aucklanduni.ac.nz}\\
  \href{http://www.linkedin.com/in/yushaoqing}{http://www.linkedin.com/in/yushaoqing} & Mobile : +64-021-151-8850 \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The University of Auckland}{Auckland, NZ}
      {Research Assistant on MPAid (Maori Pronunciation Aid)}{Nov. 2015 - Mar. 2016}
      \resumeItemListStart
        \resumeItem{Research \& Design}
          {Took over the project and studied the associated backgroud knowledge. Cleaned the legacy code and re-designed the architecture as well as the UI.}
        \resumeItem{Speech Recognition}
          {Built the Maori language model by an open-source toolkit named HTK. Automated the languae model building process by Perl and batch. Improved the recognition rate from 44.6\% to 80.4\%.}
        \resumeItem{Evaluation \& Feedback}
          {Implemented a score board to record users' pronoucing performance, analyse the recognition results and provide valuable feedbacks.}
        \resumeItem{Media}
          {Integrated the NAudio library to play and generate audio recoordings. Embedded the VLC player to play the videos of pronuncing demostrations.}
        \resumeItem{Document}
          {Uploaded and managed the source code on Github. Wrote the project wiki and  kept releasing new versions.}
        \resumeItem{Future Plan}
          {Wrote a detailed proposal about migrating the MPAid from desktop to mobile and server-hosting.}
      \resumeItemListEnd

    \resumeSubheading
      {The Second Academy of China Aerospace}{Beijing, China}
      {Leader of iTos (Intelligent Transmitting Online System) team}{Apr. 2013 and Feb. 2015}
      \resumeItemListStart
        \resumeItem{Design}
          {Designed the iTos, which can dynamically change the quality of transmitted media according to the bandwidth.}
        \resumeItem{Implementation}
          {Re-wrote the notwork component by IOCP to improve the parallel transportation. Built the media decoding/encoding/transmitting core by ffmpeg and RTSP protocol. Implemented the system sanpshot function to recover node server from fatal errors.}
        \resumeItem{Promotion}
          {Promoted and deployed the iTos to 3 military bases.}
        \resumeItem{Team Building}
          {Built an outstanding team who won the prize "the excellent team of 2014".}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{The \href{http://getskillslabs.com/}{Getskills} Website}{The University of Auckland}
      {An online education employment website developed with C\# and running on microsoft Azure server for a New Zealand company named Getskills.}
    \resumeSubItem{The \href{https://github.com/YsqEvilmax/MPAid.git}{MPAid} (Maori Pronunciation Aid)}{The University of Auckland}
      {A software on .Net platform with Maori speech recognition and evaluation system to help Maori speaker improve their pronouciation.}
    \resumeSubItem{The iTos (Intelligent Transmitting Online System)}{The Second Academy of China Aerospace}
      {A system with a high performance in massive media distributing and delivery.}
    \resumeSubItem{Children Cognitive System}{The Beihang University}
      {An education paltform which applied AR (Augmented Reality) and VR (Voice Recognization) technologies to improve the interaction between computers and children, aming to help pre-educational children effectively learn some abstract objects like thunder, wind and fog.}
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The University of Auckland}{Auckland, NZ}
      {Master of Engineering in Software Engineering;  GPA: 7.75/9.00}{Aug. 2015 -- Jun. 2016}
    \resumeSubheading
      {The Beihang University}{Beijing, China}
      {Bachelor of Engineering in Software Engineering;  GPA: 3.71/4.00}{Aug. 2009 -- Jul. 2013}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: C/C++/C\#/Java/PHP/Javascript/HTML/CSS/Perl}
      \hfill
      \textbf{Platforms}{: Windows/Linux}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
