%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\newcommand{\cvitem}[2]{\item\small{\textbf{#1}{: #2 \vspace{-2pt}}}}

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Research Assistant on MPAid (Maori Pronunciation Aid) Project} % Job title
{The University of Auckland} % Organization
{Auckland, New Zealand} % Location
{Nov. 2015 - Mar. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\cvitem {Research \& Design}
{Took over the project and studied the associated backgroud knowledge. Cleaned the legacy code and re-designed the architecture as well as the UI.}
\cvitem {Speech Recognition}
{Built the Maori language model by an open-source toolkit named HTK. Automated the languae model building process by Perl and batch. Improved the recognition rate from 44.6\% to 80.4\%.}
\cvitem {Evaluation \& Feedback}
{Implemented a score board to record users' pronoucing performance, analyse the recognition results and provide valuable feedbacks.}
\cvitem {Media}
{Integrated the NAudio library to play and generate audio recoordings. Embedded the VLC player to play the videos of pronuncing demostrations.}
\cvitem {Document}
{Uploaded and managed the source code on Github. Wrote the project wiki and  kept releasing new versions.}
\cvitem {Future Plan}
{Wrote a detailed proposal about migrating the MPAid from desktop to mobile and server-hosting.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Leader of iTos (Intelligent Transmitting Online System) Team} % Job title
{The Second Academy of China Aerospace} % Organization
{Beijing, China} % Location
{Apr. 2013 - Feb. 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\cvitem {Design}
{Designed the iTos, which can dynamically change the quality of transmitted media according to the bandwidth.}
\cvitem {Implementation}
{Re-wrote the notwork component by IOCP to improve the parallel transportation. Built the media decoding/encoding/transmitting core by ffmpeg and RTSP protocol. Implemented the system sanpshot function to recover node server from fatal errors.}
\cvitem {Promotion}
{Promoted and deployed the iTos to 3 military bases.}
\cvitem {Team Building}
{Built an outstanding team who won the prize "the excellent team of 2014".}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
