%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Projects}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{The University of Auckland} % Organization
{The MPAid (Maori Pronunciation Aid)} % Name
{Auckland, New ZeaLand} % Location
{Mar. 2016} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {A software on .Net platform with Maori speech recognition and evaluation system to help Maori speaker improve their
pronouciation.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{The University of Auckland} % Organization
{The Getskills Website} % Name
{Auckland, New ZeaLand} % Location
{Oct. 2015} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {An online education employment website developed with C\# and running on microsoft Azure server for a New Zealand
company named Getskills.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{The Second Academy of China Aerospace} % Organization
{The iTos (Intelligent Transmitting Online System)} % Name
{Beijing, China} % Location
{Feb. 2015} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {A system with a high performance in massive media distributing and delivery.}
\end{cvitems}
}
%------------------------------------------------

\cventry
{The Beijing University of Aeronautics and Astronautics} % Organization
{Children Cognitive System} % Name
{Beijing, China} % Location
{Nov. 2012} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {An education paltform which applied AR (Augmented Reality) and VR (Voice Recognization) technologies to improve the
interaction between computers and children, aming to help pre-educational children effectively learn some abstract objects
like thunder, wind and fog.}
\end{cvitems}
}
%------------------------------------------------

\end{cventries}
